Constraining the Interiors of Asteroids Through Close Encounters

### 2022-04-29 paper/appendices.tex
Responded to Julien's comments

\begin{figure*}
  \centering
  \includegraphics[width=0.49\textwidth]{figs/cad-period.pdf}\hfill
  \includegraphics[width=0.49\textwidth]{figs/cad-speed.pdf}
  \caption{Contour plots showing posterior uncertainties in the first- and second-order fit parameters as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition). The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines. The line }
  \label{fig:cad-contour}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model. \textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface. The same length scale is used in both figures.}
  \label{fig:surface-density}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.49\textwidth]{figs/cad-period.pdf}\hfill
  \includegraphics[width=0.49\textwidth]{figs/cad-speed.pdf}
  \caption{Contour plots showing posterior uncertainties in the first- and second-order fit parameters as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition). The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines. The red line represents the $\sigma(K_{\ell m})$ threshold. Cadence cutoff depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
  \label{fig:cad-contour}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model. \textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface. The same length scale is used in both figures. This new shape model successfully estimates an asteroid shape which is qualitatively consistent with the distributions extracted via models from the main text.}
  \label{fig:surface-density}
\end{figure*}
